---
title: "Kantar Competitive Review"
output: 
  html_document:
    theme: flatly
params:
  data: data
---

<style type="text/css">
.main-container {
  max-width: 80% !important;
  margin: auto;
}
</style>

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE, # Default: TRUE
  include = TRUE, # Default: TRUE
  warning = FALSE, 
  message = FALSE)

pacman::p_load(tidyverse, janitor, here, glue, DT, htmltools, magick)

dat <- params$data$image_out
spend <- params$data$spend
list_to_output <- split(dat, dat$advertiser)
# get names of each competitor for button headings
nms <- names(list_to_output)
```

This is a visual look at the digital static and gif display of the following advertisers: **`r nms`**. 

The data comes from Kantar. Unfortunately, this review *does not* contain video assets, nor does it contain rich HTML placements, both of which are hosted on a password protected server with a naming convention that doesn't contain a unique, creative ID. 

## {.tabset .tabset-pills}

### Spend Data {.tabset .tabset-pills}

#### Advertiser

```{r}
spend_table(spend, "advertiser")
```

#### Brand 

```{r}
spend_table(spend, "brand")
```

#### Product

```{r}
spend_table(spend, "product")
```

#### Media

```{r}
spend_table(spend, "media")
```

### Imagery {.tabset .tabset-pills}

#### `r nms[1]`

```{r, eval = TRUE, out.width = "90%", fig.align = "center", cache = FALSE}
# we are splitting ads into three sizes; anything with width < 600
# is appended into rows of size n
# anything larger is stacked vertically
render_images(list_to_output[[1]], size = 175, group = "a", n = 4, stack_yn = TRUE)
render_images(list_to_output[[1]], size = 300, group = "b", n = 2, stack_yn = TRUE)
render_images(list_to_output[[1]], size = 600, group = "c", n = 1, stack_yn = TRUE)
```

```{r, out.width = "90%", fig.align = "center", cache = FALSE}
files <- dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE)
ff <- files[which(str_detect(dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE), names(list_to_output)[1]))] 
knitr::include_graphics(ff)
```

#### `r nms[2]`

```{r, eval = TRUE, out.width = "90%", fig.align = "center", cache = FALSE}
# we are splitting ads into three sizes; anything with width < 600
# is appended into rows of size n
# anything larger is stacked vertically
render_images(list_to_output[[2]], size = 175, group = "a", n = 4, stack_yn = TRUE)
render_images(list_to_output[[2]], size = 300, group = "b", n = 2, stack_yn = TRUE)
render_images(list_to_output[[2]], size = 600, group = "c", n = 1, stack_yn = TRUE)
```

```{r, out.width = "90%", fig.align = "center", cache = FALSE}
files <- dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE)
ff <- files[which(str_detect(dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE), names(list_to_output)[2]))]
knitr::include_graphics(ff)
```

#### `r nms[3]`

```{r, eval = TRUE, out.width = "90%", fig.align = "center", cache = FALSE}
# we are splitting ads into three sizes; anything with width < 600
# is appended into rows of size n
# anything larger is stacked vertically
render_images(list_to_output[[3]], size = 175, group = "a", n = 4, stack_yn = TRUE)
render_images(list_to_output[[3]], size = 300, group = "b", n = 2, stack_yn = TRUE)
render_images(list_to_output[[3]], size = 600, group = "c", n = 1, stack_yn = TRUE)

```

```{r, out.width = "90%", fig.align = "center", cache = FALSE}
files <- dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE)
ff <- files[which(str_detect(dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE), names(list_to_output)[3]))]
knitr::include_graphics(ff)
```

#### `r nms[4]`

```{r, eval = TRUE, out.width = "90%", fig.align = "center", cache = FALSE}
# we are splitting ads into three sizes; anything with width < 600
# is appended into rows of size n
# anything larger is stacked vertically
render_images(list_to_output[[4]], size = 175, group = "a", n = 4, stack_yn = TRUE)
render_images(list_to_output[[4]], size = 300, group = "b", n = 2, stack_yn = TRUE)
render_images(list_to_output[[4]], size = 600, group = "c", n = 1, stack_yn = TRUE)

```

```{r, out.width = "90%", fig.align = "center", cache = FALSE}
files <- dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE)
ff <- files[which(str_detect(dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE), names(list_to_output)[4]))] 
knitr::include_graphics(ff)
```

#### `r nms[5]`

```{r, eval = TRUE, out.width = "90%", fig.align = "center", cache = FALSE}
# we are splitting ads into three sizes; anything with width < 600
# is appended into rows of size n
# anything larger is stacked vertically
render_images(list_to_output[[5]], size = 175, group = "a", n = 4, stack_yn = TRUE)
render_images(list_to_output[[5]], size = 300, group = "b", n = 2, stack_yn = TRUE)
render_images(list_to_output[[5]], size = 600, group = "c", n = 1, stack_yn = TRUE)

```

```{r, out.width = "90%", fig.align = "center", cache = FALSE}
files <- dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE)
ff <- files[which(str_detect(dir(here::here("kantar_gifs"), pattern = "*.gif", full.names = TRUE), names(list_to_output)[5]))] 
knitr::include_graphics(ff)
```
